---
title: "scREAD overlapping DEGs"
author: "Cankun Wang"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: false
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(rlist)
library(tools)
library(RVenn)
library(rjson)

# modify your directory
knitr::opts_knit$set(root.dir = "C:/Users/flyku/Documents/GitHub/scread-protocol/overlapping_genes")
setwd("C:/Users/flyku/Documents/GitHub/scread-protocol/overlapping_genes")

```



```{r,echo=F,eval=T,message=F,warning=F,error=F}
#### 
#
load("scread_db.rdata")
source("overlap_functions.R")
####
#de_meta <- de_meta[1:317,]
#dataset <- dataset[1:73,]
#save.image("scread_db.rdata")
```


```{r,echo=F,eval=T,message=FALSE,warning=F}
# GLOBAL LIST

REGION_LIST <- sort(unique(dataset$region))
CT_LIST <- sort(unique(cell_type_meta$cell_type))
CT_SHORT_LIST <- CT_LIST
CT_SHORT_LIST[CT_LIST=="Oligodendrocyte precursor cells"] <- "opc"
CT_SHORT_LIST <- tolower(substr(CT_SHORT_LIST, 1, 3))


```

# Overview

To calculate overlapping genes, these parameters are needed

The number of top genes in each AD vs control DE results (default=100)

Species (default=Human)

Brain region (e.g,Entorhinal Cortex)

DE direction (e.g, up)

Overlap threshold (for example, a gene is an overlapping gene if a should at least appeared 3 times in total 4 comparisons. Here the threshold=3)

Each section has two table: 

1. The overlapping genes in the selected region

2. The ranking information from the overlapping genes

# Human - Up-regulated

## Entorhinal Cortex

```{r,echo=F,eval=T,message=FALSE,warning=F}
# Settings
TOP <- 100
this_species <- 'Human'
this_region <- REGION_LIST[5]
this_direction <- 'up'
OVERLAP_THRES <- 3
res <- calc_overlap_list()
DT::datatable(res$list, filter = "top")
DT::datatable(res$rank, filter = "top")

```


## Prefrontal cortex

```{r,echo=F,eval=T,message=FALSE,warning=F}

# Settings
TOP <- 100
this_species <- 'Human'
this_region <- REGION_LIST[7]
this_direction <- 'up'
OVERLAP_THRES <- 4
res <- calc_overlap_list()
DT::datatable(res$list, filter = "top")
DT::datatable(res$rank, filter = "top")
```



## Superior frontal gyrus (BA8)

```{r,echo=F,eval=T,message=FALSE,warning=F}

# Settings
TOP <- 100
this_species <- 'Human'
this_region <- REGION_LIST[9]
this_direction <- 'up'
OVERLAP_THRES <- 2
res <- calc_overlap_list()
DT::datatable(res$list, filter = "top")
DT::datatable(res$rank, filter = "top")

```


## Superior parietal lobe

```{r,echo=F,eval=T,message=FALSE,warning=F}

# Settings
TOP <- 100
this_species <- 'Human'
this_region <- REGION_LIST[10]
this_direction <- 'up'
OVERLAP_THRES <- 2
res <- calc_overlap_list()
DT::datatable(res$list, filter = "top")
DT::datatable(res$rank, filter = "top")

```



# Human - Down-regulated

## Entorhinal Cortex

```{r,echo=F,eval=T,message=FALSE,warning=F}
# Settings
TOP <- 100
this_species <- 'Human'
this_region <- REGION_LIST[5]
this_direction <- 'down'
OVERLAP_THRES <- 3
res <- calc_overlap_list()
DT::datatable(res$list, filter = "top")
DT::datatable(res$rank, filter = "top")

```


## Prefrontal cortex

```{r,echo=F,eval=T,message=FALSE,warning=F}

# Settings
TOP <- 100
this_species <- 'Human'
this_region <- REGION_LIST[7]
this_direction <- 'down'
OVERLAP_THRES <- 4
res <- calc_overlap_list()
DT::datatable(res$list, filter = "top")
DT::datatable(res$rank, filter = "top")
```



## Superior frontal gyrus (BA8)

```{r,echo=F,eval=T,message=FALSE,warning=F}

# Settings
TOP <- 100
this_species <- 'Human'
this_region <- REGION_LIST[9]
this_direction <- 'down'
OVERLAP_THRES <- 2
res <- calc_overlap_list()
DT::datatable(res$list, filter = "top")
DT::datatable(res$rank, filter = "top")

```


## Superior parietal lobe

```{r,echo=F,eval=T,message=FALSE,warning=F}

# Settings
TOP <- 100
this_species <- 'Human'
this_region <- REGION_LIST[10]
this_direction <- 'down'
OVERLAP_THRES <- 2
res <- calc_overlap_list()
DT::datatable(res$list, filter = "top")
DT::datatable(res$rank, filter = "top")

```



# Session Infomation

```{r}
sessionInfo()
```
